A Simplified Spectral Deferred Correction Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2020-10-17 simplified_sdc_intro/paper.tex
add some aux stuff

We solve the Euler equations for compressible, reacting flow.  We'll
focus on one-dimensional flow for this description, and the system
appears as:
\begin{equation}
\frac{\partial \Uc_t}{\partial t}  + \frac{\partial \Fb^\xv (\Uc)}{\partial x} = \Sc(\Uc)
\end{equation}
where
\begin{equation}
\Uc = \left ( \begin{array}{c}
           \rho \\
           \rho X_k \\
           \rho u \\
           \rho E \end{array}\right )
\end{equation}
are the conserved fluid quantities: mass density, $\rho$, velocity, $u$,
specific total energy, $E$, and nuclear
species mass fractions, $X_k$.  The specific total energy relates to
the specific internal energy as $E = e + u^2/2$.  The
corresponding fluxes are
\begin{equation}
\Fb^\xv (\Uc) = \left ( \begin{array}{c}
   \rho u \\ \rho X_k u \\ \rho u u + p \\  \rho u E + u p
   \end{array} \right )
\end{equation}
Here the pressure, $p$, enters, and is found via the equation of state,
\begin{equation}
p = p(\rho, X_k, e)
\end{equation}

>>>>

We solve the Euler equations for compressible, reacting flow.  We'll
focus on one-dimensional flow for this description, and the system
appears as:
\begin{equation}
\frac{\partial \Uc_t}{\partial t}  + \frac{\partial \Fb^\xv (\Uc)}{\partial x} = \Sc(\Uc)
\end{equation}
where
\begin{equation}
\Uc = \left ( \begin{array}{c}
           \rho \\
           \rho X_k \\
           \rho \alpha_l \\
           \rho u \\
           \rho E \end{array}\right )
\end{equation}
are the conserved fluid quantities: mass density, $\rho$, velocity,
$u$, specific total energy, $E$, and nuclear species mass fractions,
$X_k$, and auxiliary composition variables, $a_l$.  The mass fractions
are constrained to sum to 1, $\sum_k X_k = 1$, but no such constraint
exists on the auxiliary variables.  The specific total energy relates
to the specific internal energy as $E = e + u^2/2$.  The corresponding
fluxes are
\begin{equation}
\Fb^\xv (\Uc) = \left ( \begin{array}{c}
   \rho u \\
   \rho X_k u \\
   \rho \alpha_l u \\
   \rho u u + p \\
   \rho u E + u p
   \end{array} \right )
\end{equation}
Here the pressure, $p$, enters, and is found via the equation of state.  For a system
where the composition is completely specified by the mass fractions, $X_k$, the equation
of state would take the form:
\begin{equation}
p = p(\rho, X_k, e)
\end{equation}
However, as we'll see shortly, when we use the NSE table, we are using
the results of a much larger network then can be represented by the
mass fractions, and in this case, we rely on the auxiliary composition
variables, $\alpha_l$, to describe the state of the composition, and
our EOS has the form:
\begin{equation}
p = p(\rho, \alpha_l, e)
\end{equation}
